LaMachine: A meta-distribution for NLP software

### 2019-01-28 docs/lamachine_clarin2018.tex
paper update

\section{Case studies}
\label{sec:case}

\subsection{Text Mining for Health Inspection}

@@

\subsection{Workshop: Cataloguing of Textual Cultural Heritage Objects}

@@

For this workshop, computing power was purchased at SURFsara, a collaborative organization for ICT in Dutch education
and research. Subsequently, we had the ability to create Virtual Machines on their hosting platform. For this workshop
we had twelve participants and decided to create a single multi-core and hih memory VM to share amongst the
participants.

As recommended by SURFsara, we opted for one of their default Linux images based on Ubuntu 18.04, and we bootstrapped
the local installation flavor of LaMachine inside that VM.

>>>>

\section{Case studies}

\subsection{Text Mining for Health Inspection}
\label{sec:case}

@@

\subsection{Workshop: Cataloguing of Textual Cultural Heritage Objects}
\label{sec:case2}

@@

For this workshop, computing power was purchased at SURFsara, a collaborative organization for ICT in Dutch education
and research. Subsequently, we had the ability to create Virtual Machines on their hosting platform. For this workshop
we had twelve participants and decided to create a single multi-core and high memory VM to share amongst the
participants.

As recommended by SURFsara, we opted for one of their default Linux images as a basis for the VM, based on Ubuntu 18.04,
instead of providing a LaMachine VM image directly like we did in \section{sec:case}. This was recommended because their image
was already preconfigured to integrate nicely with their cloud environment. Inside this VM we simply bootstrapped the local
installation flavour of LaMachine.  Here we benefit from the flexibility LaMachine offers because of its various
flavours, and regardless of the flavour, the resulting installations are always functionally equivalent. The local
environment flavour had the added bonus of not being in anyone's way in case any of the twelve workshop participants did
not want to use LaMachine, considering it needs to be explicitly activated prior to usage.
